---
title: "HW4 - Question 4"
author: "Marquette Jones"
date: ""
format:
  pdf:
    embed-resources: true
    theme: cosmo
    code-line-numbers: true
    number_examples: true
    number_sections: true
    number_chapters: true
    linkcolor: blue
editor: visual
fig-cap-location: top
---

Does NFL Conference help explain yards per game gained by teams?  Data retrieved from: https://www.espn.com/nfl/stats/team


```{r}
library(readxl)
nfl_xl <- read_excel("C:\\Users\\Mark\\Desktop\\Stats_Homework\\Homework4\\NFL_Stats.xlsx")
nfl_xl$CONF <- as.factor(nfl_xl$CONF)
nfl_xl
```
```{r}
library(ggplot2)
ggplot(nfl_xl, aes(x = CONF, y = YPG_AVG)) + geom_boxplot()

```
```{r}
library(car)
nfl_model <- aov(YPG_AVG ~ CONF, data = nfl_xl)
summary(lm(nfl_model))

nfl_fits <- fitted(nfl_model)
nfl_res <- residuals(nfl_model)

shapiro.test(nfl_res)
leveneTest(YPG_AVG ~ CONF, data = nfl_xl)
qf(0.95, 1, 30)
```
Comment:  

Normality:  The large p-value from the Shapiro test validates normality. 


Equal Variance: The large p-value supports the assumption of equal variances.


The p-value is higher than the critical value, so we cannot reject the null hypothesis, so we assume that the NFL conference you are in does not have a significant effect on the YPG averaged of a team. Also, the F-observed value is less than the critical F-value, which also suggests that there is no significant difference in sample averages.

